Reproducible Research: Peer Assessment 1
========================================
Fabian Linzberger - https://github.com/lefant/RepData_PeerAssessment1

## Loading and preprocessing the data
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

1. Make a histogram of the total number of steps taken each day

```{r}
steps.date <- aggregate(steps ~ date, data = activity, FUN=sum)
barplot(steps.date$steps, names.arg=steps.date$date, xlab="date", ylab="steps")
```

2. Calculate and report the **mean** and **median** total number of
   steps taken per day

```{r}
mean(steps.date$steps)
median(steps.date$steps)
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. `type = "l"`) of the 5-minute
   interval (x-axis) and the average number of steps taken, averaged
   across all days (y-axis)

```{r}
steps.interval <- aggregate(steps ~ interval, data = activity, FUN=sum)
plot(steps.interval, type="l")
```

2. Which 5-minute interval, on average across all the days in the
   dataset, contains the maximum number of steps?

```{r}
steps.interval$interval[which.max(steps.interval$steps)]
```


## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
